INTELLIGENT SYSTEMS

### 2021-04-07 paper_5.tex
finish 5.3.3

\subsubsection{Initial CNN Architecture}
The length of the input is normalized before it can end up on CNN. Each 
sequence S is divided into U sub-sequences $ s_i $, where $ 1 \leq i \leq U $. However, 
a sequence is divided into windows having length L, with an overlap of 0\%, 
where each signal size defines a specific input channel. The number D of 
channels is useful for defining the 1 x N x D dimension of the filter of the 
first layer, where N indicates the dimension of the convolution. The proposed 
convolutional network is composed of 4 convolutional layers and a gradually 
increasing number of filters. After convolution there are elements such as 
ReLU, batch normalization (useful for faster learning) and max pooling. After 
the last convolutional layer, the average is chosen as a pooling operation. 
Then dropout and fully-connected layers are added with a number of outputs 
equal to the required classes. The last layer is composed of the Softmax 
normalization function which returns the probability distribution of each class. 
To train the model, a cross-entropy is used as a loss function.
\begin{figure}[htbp]
    \centering
    \includegraphics[width = 1 \linewidth]{images/paper5/architecture.png}
    \centering
    \caption{Pipeline for multi-task and multi-sensor learning in a gait-based system}
    \label{fig:pipeline}
\end{figure}

\subsubsection{Multi-task Approach}

>>>>

\subsubsection{Initial CNN Architecture}
The length of the input is normalized before it can end up on CNN. Each 
sequence S is divided into U sub-sequences $ s_i $, where $ 1 \leq i \leq U $. However, 
a sequence is divided into windows having length L, with an overlap of 0\%, 
where each signal size defines a specific input channel. The number D of 
channels is useful for defining the 1 x N x D dimension of the filter of the 
first layer, where N indicates the dimension of the convolution. The proposed 
convolutional network is composed of 4 convolutional layers and a gradually 
increasing number of filters. After convolution there are elements such as 
ReLU, batch normalization (useful for faster learning) and max pooling. After 
the last convolutional layer, the average is chosen as a pooling operation. 
Then dropout and fully-connected layers are added with a number of outputs 
equal to the required classes. The last layer is composed of the Softmax 
normalization function which returns the probability distribution of each class. 
To train the model, only for the identification task, a cross-entropy is used 
as a loss function.
\begin{figure}[htbp]
    \centering
    \includegraphics[width = 1 \linewidth]{images/paper5/architecture.png}
    \centering
    \caption{Pipeline for multi-task and multi-sensor learning in a gait-based system}
    \label{fig:pipeline}
\end{figure}

\subsubsection{Multi-task Approach}
The aim is to training a deep multi-task model (DTM). In order to do this, 
there must be a set of tuples $ I = (s_i, y_i^m, y_1^1, ..., y_i^T) $ where $ y_i^m $ is the label 
of the main task, $ y_i^t $, with $ t \in [1,T] $, is the label for each auxilary task. 
Each individual task has its own loss function \emph{L}. The loss function (\ref{loss-function}) is 
calculated on each sub-sequence \emph{s} and is formed by the product of each single 
loss function, of each task, with the weights ($ \lambda $)  associated at each task.
\begin{eqnarray}\label{loss-function}
    \emph{$ L_{DTM} (g(s,\theta), Y) $} & = & \lambda_{id}L_{id}(\hat{y}^{id}, y^{id}) \nonumber \\
                                        &   & + \lambda_{age}L_{age}(\hat{y}^{age}, y^{age}) \nonumber \\
                                        &   & + \lambda_{gender}L_{gender}(\hat{y}^{gender}, y^{gender}) 
\end{eqnarray}
Where $ Y = (y^{id}_i, y^{age}_i, y^{gender}_i) $ and $ L_{id}, L_{age}, L_{gender} $ are the loss functions of 
each tasks. As for the identity and gender tasks, their loss function is the 
cross-entropy and is calculated with the formula \ref{cross-entropy}.
\begin{equation}\label{cross-entropy}
    \emph{$ L_m(\hat{y}, c) $} = -\hat{y}_c+\log\sum^K_{k=1}e^{\hat{y}k} 
\end{equation}
Where $ \hat{y} $ is the ouput vector of the network, $ \hat{y}_c $ is the output for target class, 
$ \hat{y}_k $ is the \emph{k}-th component of the output vector, \emph{c} is the ground-truth class 
and \emph{K} is the total number of classes.
